 

### 2021-07-27 vertical-thermal-review.Rmd
updated

The interannual climate sensitivity of annual woody growth can be determined through analysis of tree-ring increments.
While it is generally accepted that large, exposed trees display the greatest climate sensitivity and are therefore best for climate reconstructions (**REFS--KAT**), only a relatively limited number of studies have directly examined drought- or temperature- sensitivities as a function of tree size.
These have generally found greater sensitivity to low precipitation or high temperatures among large/ canopy trees [**Fig. `r fig_treerings`**, @mcgregorTreeHeightLeaf2021; @anderson-teixeiraJointEffectsClimate2021] , corroborating evidence from forest censuses that larger trees tend to undergo larger growth declines during drought [@bennettLargerTreesSuffer2015].
Despite the potential for shorter trees in open forests to experience greater environmental stress [*Fig. `r fig_schematic`b*; **REFS**], this pattern has been observed in open as well as closed-canopy forests [@bennettLargerTreesSuffer2015; @anderson-teixeiraJointEffectsClimate2021].

>>>>

The interannual climate sensitivity of annual woody growth can be determined through analysis of tree-ring increments.
While it is generally accepted that large, exposed trees display the greatest climate sensitivity and are therefore best for climate reconstructions (**REFS--KAT**), only a relatively limited number of studies have directly examined drought- or temperature-sensitivities as a function of tree size.
These have generally found greater sensitivity to low precipitation or high summer temperatures among larger, more exposed trees [**Fig. `r fig_treerings`**, @mcgregorTreeHeightLeaf2021; @anderson-teixeiraJointEffectsClimate2021] , corroborating evidence from forest censuses that larger trees tend to undergo larger growth declines during drought [@bennettLargerTreesSuffer2015].
Despite the potential for shorter trees in open forests to experience greater environmental stress [*Fig. `r fig_schematic`b*; **REFS**], this pattern has been observed in open as well as closed-canopy forests [@bennettLargerTreesSuffer2015; @anderson-teixeiraJointEffectsClimate2021].
